---
title: "jh2w1p4"
output: html_document
date: '2022-05-30'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## week 1 (p4)
### Textuak Data Formats

* *dumping* and *dputing* are useful because the resulting textual format is editable, and in the case of corruption, potentially recoverable.
* Unlike writing out a table or csv file, *dump* or *dput* preserve *metadata* (sacrificing some readability), so that another user doesn't have to specify it all over again.
* Textual formats can work much better with version control programs like subversion/git which can only track changes meaningfully in text files.
* Textual formats can be longer-lived, i.e. if there is corruption somewhere in the file, it can be easier to fix the problem.
* Textual formats adhere to the *Unix Philosophy*
* A downside is that the format is not very space-efficient
* Corresponding reading functions are *source* and *dget*

### dput-ting R Objects
Another way to pass data is by deparsing the R object with *dput* and reading it back in using *dget*:

```{r}
y <- data.frame(a= 1, b="a")
dput(y)
dput(y, file = "y.R")
new.y <- dget("y.R")
new.y
```

### Dumping R objects
Multiple objects can be deparsed using the *dump* function and read back in via *source*:

```{r}
x <- "foo"
z <- data.frame(a= 1, b="a")
dump(c("x","z"), file = "data.R")
rm(x,z)
source("data.R")
z
x
```

### Interfaces to the Outside World
Data are read in using *connection* interfaces. Connections can be made to files (most common) or to other exotic things:

* *file*, opens a connection to a file,
* *gzfile*, opens a connection to a file compressed with *gzip*,
* *bzfile*, opens a connection to a file compressed with *bzip2*,
* *url*, opens a connection to a webpage

Lots of functions (like *read.table*) use a connection to a file behind the scenes

### File Connection
```{r}
str(file)
```
file Function arguments

* *description* is the name of the file,
* *open* is code indicating
  + *r* - read-only
  + *w* - writing (and initializing) a file,
  + *a* - appending,
  + *rb*, *wb*, *ab* - reading, writing or appending in binary mode (Windows)
  
Other options are not that important right now

### Connections
Connections are powerful tools that let you navigate files or other external objects. In practice, we often don't need to deal with the connection interface directly:

```{r}
con <- file("foo.txt", "r")
data <- read.csv(con)
close(con)
```

is the same as:
```{r}
data <- read.csv("foo.txt")
```

Sometimes it can be useful. Like if you want to read parts of a file:

```{r}
#con <- gzfile("words.gz")
#x <- readLines(con, 10)
#x
```
*writeLines* takes a character vector and writes each element one line at a time to a text file.

*readLines* can be useful for reading in lines of webpages

```{r}
# This might take time
con <- url("http://jhsph.edu", "r")
x <- readLines(con)
#head(x)
```
The *url* function is useful for creating a connection to webpages

