---
title: "jh2w1p4"
output: html_document
date: '2022-05-30'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## week 1 (p4)
### Textuak Data Formats

* *dumping* and *dputing* are useful because the resulting textual format is editable, and in the case of corruption, potentially recoverable.
* Unlike writing out a table or csv file, *dump* or *dput* preserve *metadata* (sacrificing some readability), so that another user doesn't have to specify it all over again.
* Textual formats can work much better with version control programs like subversion/git which can only track changes meaningfully in text files.
* Textual formats can be longer-lived, i.e. if there is corruption somewhere in the file, it can be easier to fix the problem.
* Textual formats adhere to the *Unix Philosophy*
* A downside is that the format is not very space-efficient
* Corresponding reading functions are *source* and *dget*

### dput-ting R Objects
Another way to pass data is by deparsing the R object with *dput* and reading it back in using *dget*:

```{r}
y <- data.frame(a= 1, b="a")
dput(y)
dput(y, file = "y.R")
new.y <- dget("y.R")
new.y
```

### Dumping R objects
Multiple objects can be deparsed using the *dump* function and read back in via *source*:

```{r}
x <- "foo"
z <- data.frame(a= 1, b="a")
dump(c("x","z"), file = "data.R")
rm(x,z)
source("data.R")
z
x
```

