---
title: "notes_w1"
author: "Sashin"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Week 1
### data types -- Matrices
Matrices are vectors with a dimension attribute. The dimension attribute
is itself an integer vector (nrow, ncol)
Matrices can be created via the matrix function.Values can be instantiated here,
they are inserted by column first

A matrix can also be created by creating the dimension attribute on a vector.
We saying we want to change this vector into a matrix of n cols and m rows.

```
m <- matrix(start:end,nrow = 2, ncol = 4)

m <- 1:6
dim(m) <- c(2,3)
```

Another way to create a matrix is by binding cols/rows via cbind/rbind
```
x<-3:5
y<-10:13
cbind(x, y)
rbind(x, y)
```


### Factors
Factors are a special type of vector that is used to represent categorical 
data.
Factors can be unordered or ordered. 
One can think of a factor as an int value where each value has a label.
- Factors are treated specially by modelling functions like lm() and glm()
- Using factors with labels is better than using integers because factors
are self describing; having a variable that has value "Male" or "Female"
is better than having a variable that has values 1 or 2.

created via factor fn, by passing a character vector. table fn can give
us a frequeny count of results. unclass fn strips out the class (text).
attr fn can be used to find the levels options.

```{r factors}
x <- factor(c("yes", "no", "yes", "yes", "yes"))
table(x)
unclass(x)
attr(x,"levels")
```

The order of the levels can be set using the levels argument to factors.
This can be important in linear modelling because the first level is used as
the baseline level. Default is alphabetical
```{r}
 x <- factor(c(c("yes", "no", "yes")), levels = c("yes", "no"))
```

