---
title: "jhu2w1p2"
author: "Sashin"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Week 1 (p2)
### Data Frames
This is a key data type in R. It is used to store tabular data.It is very
important
- They are represented as a special type of list, where every element of the
list has to have the same length
- Each element of the list can be thought of as a column and the length
of the list is the number of rows.
- Unlike matrices, data frames can store different classes of objects in each
column (like lists) (matrices must have every element be the same class)
- Data Frames also have a special attribute called row.names
- Data Frames are usually created by called read.table() or read.csv()
- Can be converted to a matrix by calling data.matrix()

```{r data frame}
df <- data.frame(foo = 1:4, bar = c(T,T,F,F))
df
nrow(df)
ncol(df)
```
No row names specified


### Names
R objects (all of them) can also have names , which is very useful for writing
readable code and self-describing objects. By default there are no names.
We can assign names using the names function. This function can also return 
the names.
```{r}
x3 <- 1:3
names(x3)
names(x3) <- c("foo","bar","norf")
x3
names(x3)
```

Lists can also have names, this can be done inside the list function when
creating the list:
```{r}
l1 <- list(a = 1, b = 2, c = 3)
l1
```

Matrices can also have names. They can be set via the dimnames() function.
We pass it a list where the first element is a vector of row names, and the
second element is a vector of column names

```{r}
m1 <- matrix(1:4, nrow=2, ncol=2)
dimnames(m1) <- list(c("a","b"), c("c", "d"))
m1
```

