---
title: "jh2w1p5.3"
output: html_document
date: '2022-05-30'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## week 1 (part 5.3)
### Subsetting - Matrices
Matrices can be subsetted in the usual way with (i,j) type indices:
```{r}
xm1 <- matrix(1:6, 2, 3)
xm1
xm1[1,2]
xm1[2,1]
```
Indices can also be missing:
```{r}
xm2 <- matrix(1:6, 2, 3)
xm2
xm2[1,] # first row returns a vector
xm2[,2] # second col returns vector
```

By default, when a single element of a matrix is retrieved,  it is returned as a vector of length 1 rather a 1x1 matrix. This behavior can be turned off by setting *drop* = false. *drop* drops the dimension:
```{r}
xm3 <- matrix(1:6, 2, 3)
xm3
xm3[1,2, drop = FALSE]
```

Similarly, subsetting a single column or a single row will give you a vector, not a matrix (by default):
```{r}
xm4 <- matrix(1:6, 2, 3)
xm4
xm4[1, , drop = FALSE]
```


## week 1 (part 5.4)
### Subsetting - Partial Matching
Partial matching of names is allowed with [[]] and $ operators:
```{r}
xl5 <- list(aardvark = 1:5)
xl5$a
xl5[["a"]]
xl5[["a", exact=FALSE]]
```
* Useful when working in the command line, makes typing quicker


### Subsetting -- Removing missing values
Removing NA values. Most realistic data has alot of missing values. Hence a common task is removing this. The common pattern is to create logical vector that points out where the na's are so you can remove them by subsetting:
```{r}
v1 <- c(12, 21, NA, NA, 34, NA)
v1
bad <- is.na(v1)
bad
v1[!bad]
```

What if there are multiple things and you want to take the subset with no missing values:
```{r}
v2 <- c(1, 2, NA, 4, NA, 5)
v2
v3 <- c("a", "b", NA, "d", NA, NA)
v3
good <- complete.cases(v2, v3) # whcich positions for both vectors are non-missing
good
v2[good]
v3[good]
```
*complete.cases* can also be used to remove rows from data frames that have missing values:
```{r}
# airquality[1:6, ]
# good <- complete.cases(airquality)
# airquality[good, ][1:6, ]

```