---
title: "jh2w1p5"
output: html_document
date: '2022-05-30'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## week 1 (part 5.1)
### Subsetting - Basics

There are a number of operators that can be used to extract subsets of R objects:

* [ always returns an object of the same class as the original; can be used to select more than one element (there is one exception) (covered later)
* [[ is used to extract elements of a list or data frame; it can only be used to extract a single element and the class of the returned object will not necessarily be a list or a data frame.
* $ is used to extract elements of a list or a data frame by name; semantics are similar to that of [[

```{r}
xa <- c("a", "b", "c", "c", "d", "a")
xa[1]
xa[2]
xa[1:4]
xa[xa > "a"]
u <- xa > "a"
u
xa[u]
```

## week 1 (part 5.2)
### Subsetting - Lists
Little different than vectors, since the double bracket or dollar sign operators can also be used.

```{r}
xl <- list(foo=1:4, bar = 0.6)
xl[1]     # returns list contain name and sequence
xl[[1]]   # returns just the sequence
xl$bar    # returns element whose name matches bar
xl[["bar"]]
xl["bar"] # returns a list with value 0.6 named bar
```

You need to use the single bracket operator to extract multiple elements of a list:
```{r}
xl2 <- list(foo = 1:4, bar = 0.6, baz = "hello")
xl2[c(1, 3)]    # pass vector of 1 and 3 and returns list of elements in these positions
```

The [[]] operator can be used with computed indices, $ operator can only be used with literal names
```{r}
xl2 <- list(foo = 1:4, bar = 0.6, baz = "hello")
name <- "baz" 
xl2[[name]]   # computed index of "baz"
xl2$name      # doesnt exist
xl2$baz
```

The [[]] operator can take an integer sequence. 
```{r}
xl2 <- list(a = list(10, 12, 14), b = c(3.14, 2.81))
xl2[c(1, 3)]
xl2[[1]][[3]]
xl2[[c(2,1)]]
```
