---
title: "jhu2w1p6"
output: html_document
date: '2022-05-30'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## week 1 (part 6)
### Vectorized operations

Many operations in R are *vectorized*, making code more efficient, concise, and easier to read:
```{r}
x <- 1:4; y<- 6:9
x
y
x+y
x>2
x>=2
x=8
x*y
x/y
```

Allows for easily doing vector addition, division, multiplacation. Can also run boolean checks on all elements in the vector.


We can similarly add, subtract, *, / matrices:

```{r}
m1 <- matrix(1:4,2,2)
m2 <- matrix(rep(10,4),2,2)
m1
m2
m1 + m2
m1 * m2 # element wise *
m1 / m2
m1 %*% m2 # true matrix multiplacation

```



```{r}

#mean(ozone[!is.na(ozone)])
#hw1[hw1$Ozone > 31 & hw1$Temp>90, ]
```
hw1 <- read.csv("hw1_data.csv")

17. mean(hw1$Ozone[!is.na(hw1$Ozone)])
18. sub <- hw1[hw1$Ozone > 31 & hw1$Temp>90, ]
mean(sub$Solar.R[!is.na(sub$Solar.R)])

19. sub2 <- hw1[hw1$Month == 6,]
mean(sub2$Temp[!is.na(sub2$Temp)])

20.
sub3 <- hw1[hw1$Month == 5,]
max(sub3$Ozone[!is.na(sub3$Ozone)])
